\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/letter.tex
Update Dec 25 11.30

\textcolor{blue}{The syntactic metrics commonly used by other approaches count the number of differences wrt the GTM and normalize by the total number of possible preconditions and effects. This produces an optimistic metric since the set of possible preconditions and effects is usually much larger than the set of learned ones, resulting in low error rates even when the model is largely flawed. In contrast, precision and recall normalize by the size of the model, removing this problem. Furthermore, precision and recall give a notion of soundness and completeness by splitting the differences into extra and missing preconditions/effects. We have added some paragraphs to section 5 to better explain these concepts.}

\textcolor{blue}{As the reviewer points out, the learning will create a model that explains all the training traces. There is, however, no guarantee that the training traces are able to capture all the dynamics of the domain. This is specially true for scenarios with low observability like the ones explored in this paper. Hence, it is always interesting to measure how well the learned model is able to explain new plan traces.}

>>>>

\textcolor{blue}{The syntactic metrics commonly used by other approaches count the number of differences wrt the GTM and normalize by the total number of possible preconditions and effects. This gives rise to an optimistic measure of the error since the set of possible preconditions and effects is usually much larger than the size of the actual GTM, resulting in low error rates even when the model is largely flawed. In contrast, precision and recall normalize by the size of the GTM, thus removing this problem. Furthermore, precision and recall provide an intuitive notion of soundness and completeness, respectively; whereas a sound model is interpreted as a model in which all preconditions and effects are correct wrt the GTM, a complete model is one in which no precondition or effect is missing. We have added some paragraphs to section 5 to better explain these concepts.}

\textcolor{blue}{As the reviewer points out, \FAMA will create a model that explains all the training traces because it is a satisfying approach (that satisfies all the training samples) and so the training error is 0. There is, however, no guarantee that the training traces are able to capture the whole dynamics of the domain. This is specially true for scenarios with low observability like the ones explored in this paper. Hence, it is always interesting to measure how well the learned model is able to explain a new set of plan traces.}
